The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-03-31 ms.Rmd
Split Merow into a plan and working workflow for now.

```{r merowworkflow, eval = FALSE}
Merow_Silander <- workflow(
    occurrence = CarolinaWrenPO,
    covariate = ...,
    process = ...,
    model = list(LogisticRegression, MaxEnt, MaxLike),
    output = ...)
```

>>>>

```{r merowpreamblel, eval = TRUE, echo = FALSE}

# Load the data into the global environment
data(carw, envir = environment())

rl <- lapply(carw.data$raster.data, function(x) {
   m <- matrix(x, nrow=carw.data$dim[1], ncol=carw.data$dim[2],
               byrow=TRUE)
   r <- raster(m)
   extent(r) <- c(-124.83, -66.67, 24.61, 49.41)
   r
})

# Stack and name them
CarolinaRasters <- stack(rl[[1]], rl[[2]], rl[[3]], rl[[4]], rl[[5]], rl[[6]])
names(CarolinaRasters) <- names(carw.data$raster.data)

```{r merowWorkingCopy, eval = TRUE}

Merow_Silander <- workflow(
    occurrence = Chain(LocalOccurrenceData('occurrenceType = 'presence' ),
                       LocalOccurrenceData(occurrenceType = 'presence/absence', externalValidation = TRUE)),
     covariate = LocalRasterData('CarolinaRasters'),
       process = Chain(Transform(trans = 'square', replace = FALSE), 
                       Background(n = 10000)),
         model = list(LogisticRegression, MaxEnt, MaxLike),
        output = Chain(PerformanceMeasures, PointBiserialCorr, PrintMap)

```{r merowworkflow, eval = FALSE}

Merow_Silander <- workflow(
    occurrence = Chain(LocalOccurrenceData(occurrenceType = 'presence' ),
                       LocalOccurrenceData(occurrenceType = 'presence/absence', externalValidation = TRUE)),
     covariate = LocalRasterData('CarolinaRasters'),
       process = Chain(Transform(trans = 'square', replace = FALSE), 
                       Background(n = 10000)),
         model = list(LogisticRegression, MaxEnt, MaxLike),
        output = Chain(PerformanceMeasures, PointBiserialCorr, PrintMap, Coefficients)
```
